---
title: "endothelial-RPE-ligand-target-analysis"
author: "yincy"
date: "5/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages  
```{r, message=FALSE, warning=FALSE}
library(nichenetr)
library(tidyverse)
library(RColorBrewer)
library(cowplot)
library(monocle3)
library(ggridges)
library(igraph)
library(circlize)
```

# load ligand target matrix  
```{r}
ligand_target_matrix <- readRDS(file = "/home/yincy/git/Data/NicheNet/data/ligand_target_matrix.rds")
ligand_target_matrix %>% dim()
ligand_target_matrix %>% .[1:5, 1:5]
```

# cd31 enriched donor 4 choriocapillaris endothelial expressed genes  
```{r}
donor4_expression <- read.table(file = "/home/yincy/git/Data/AMD-related/AMD-single-cell/GSM4037987/GSM4037987_macula_donor_4_enriched_expression.tsv.gz", 
                                sep = " ", 
                                header = T, 
                                stringsAsFactors = F)
donor4_expression %>% dim()
donor4_expression %>% .[1:5, 1:5]

donor4_expression <- donor4_expression[, -1]
donor4_cell_meta <- donor4_expression[, c(1:3)]

donor4_expression_table <- donor4_expression[, -c(1:3)] %>% 
  t() %>% 
  magrittr::set_colnames(donor4_expression$barcode)

# choriocapillaris endothelial  
donor4_choriocapillaris_endothelial <- donor4_expression_table[, donor4_cell_meta$final_cluster_labels == 7]
donor4_choriocapillaris_endothelial %>% dim()
expressed_genes_choriocapillaris_endothelial <- rownames(donor4_choriocapillaris_endothelial)[apply(donor4_choriocapillaris_endothelial, 1, function(x) mean(x > 0) > 0.1)]
```


# background genes
```{r, cache=TRUE}
expressed_gene_RPE_Early_AMD <- read.table(file = "/home/yincy/git/Data/AMD-related/GSE99248/GSE99248_Early_anti_sense_expressed_genes.txt", 
                                           sep = "\t", 
                                           header = T)

background_expressed_genes <- intersect(expressed_gene_RPE_Early_AMD$geneSymbol, ligand_target_matrix %>% rownames()) %>% unique()
```


# gene of interest   
```{r}
goi <- readRDS(file = "/home/yincy/git/R/Retina/amd-related-genes/amd_related_genes.rds") %>% 
  append(readRDS(file = "/home/yincy/git/R/Retina/amd-related-genes/amd_genes_in_cellpress.rds")) %>% 
  append(readRDS(file = "/home/yincy/git/R/Retina/amd-related-genes/ng_table5.rds")) %>% 
  unique()

goi_expressed <- intersect(goi, expressed_gene_RPE_Early_AMD$geneSymbol) %>% unique()
```

# potential ligands
```{r}
lr_network <- readRDS(file = "/home/yincy/git/Data/NicheNet/data/lr_network.rds")
ligands <- lr_network %>% pull(from) %>% unique()
expressed_ligands_choriocapillaris_endothelial <- intersect(ligands, expressed_genes_choriocapillaris_endothelial)

receptors <- lr_network %>% pull(to) %>% unique()
expressed_receptors_rpe_amd <- intersect(receptors, expressed_gene_RPE_Early_AMD$geneSymbol)

lr_network_expressed <- lr_network %>% 
  dplyr::filter(from %in% expressed_ligands_choriocapillaris_endothelial, to %in% expressed_receptors_rpe_amd)

potential_ligands <- lr_network_expressed %>% pull(from) %>% unique()
potential_ligands %>% head()
```


# ligand activity   
```{r}
ligand_activities <- predict_ligand_activities(geneset = goi_expressed, 
                                               background_expressed_genes = background_expressed_genes, 
                                               ligand_target_matrix = ligand_target_matrix, 
                                               potential_ligands = potential_ligands)

ligand_activities %>% 
  arrange(-pearson)
```


```{r}
ligand_activities %>% 
  pull(pearson) %>% 
  hist(breaks = seq(min(ligand_activities$pearson), max(ligand_activities$pearson), length.out = 30),
       main = "The distribution of Pearson value", 
       col = 'orange', 
       border = "grey")

abline(v = ligand_activities %>% 
         arrange(desc(pearson)) %>% 
         pull(pearson) %>% .[15], col = "red", lty = 2, lwd = 2)
```

```{r}
best_upstream_ligands <- ligand_activities %>% 
  arrange(-pearson) %>% 
  head(n = 15) %>% 
  pull(test_ligand)
```

```{r}
cols <- colorRampPalette(colors = brewer.pal(n = 9, name = "Blues")[5:9])

ligand_activities_heatmap <- ligand_activities %>% 
  arrange(-pearson) %>% 
  filter(test_ligand %in% best_upstream_ligands) %>% 
  ggplot(aes(x = reorder(test_ligand, pearson), y = factor(1))) +
  geom_tile(aes(fill = pearson), linetype = 1) +
  coord_flip() +
  scale_fill_gradient(name = NULL, low = "whitesmoke", high = "darkorange") +
  scale_y_discrete(name = NULL, expand = c(0, 0), labels = NULL, breaks = NULL) +
  scale_x_discrete(name = NULL, expand = c(0, 0)) +
  ggtitle(label = "ligand activity") +
  theme(plot.title = element_text(hjust = 0.5, size = 10))

ligand_activities_heatmap
saveRDS(object = ligand_activities_heatmap, 
        file = "/home/yincy/git/R/Retina/res/ligand_activity_heatmap.rds")
```

# Assess how well top-ranked ligands can predict gene of interest  
build a multi-ligand model use all-top-ranked ligands to predict whether a gene belongs to the AMD-related gene of not. 
```{r}
k = 3
n = 5

goi_expressed_assess <- append(x = goi_expressed, 
                               values = sample(goi_expressed, k - (length(goi_expressed) %% k)))

amd_genes_prediction_top15_list <- seq(n) %>% 
  lapply(assess_rf_class_probabilities, 
         folds = k, 
         geneset = goi_expressed_assess, 
         background_expressed_genes = background_expressed_genes, 
         ligands_oi = best_upstream_ligands, 
         ligand_target_matrix = ligand_target_matrix)
```


Evaluate now how well the target gene probabilies accord to the gene set assignments  
```{r}
target_prediction_performances_cv <- amd_genes_prediction_top15_list %>% 
  lapply(classification_evaluation_continuous_pred_wrapper) %>% 
  bind_rows() %>% 
  mutate(round = seq(1:nrow(.)))
```

```{r}
target_prediction_performances_cv$auroc %>% mean()
target_prediction_performances_cv$aupr %>% mean()
target_prediction_performances_cv$pearson %>% mean()
```

Evaluate now whether genes belonging to the gene set are more likely to be top-predicted. We will look at the top 5% of predicted targets here.  
```{r}
target_prediction_performances_discrete_cv <- amd_genes_prediction_top15_list %>% 
  lapply(calculate_fraction_top_predicted, quantile_cutoff = 0.95) %>% 
  bind_rows() %>% 
  ungroup() %>% 
  mutate(round = rep(1:length(amd_genes_prediction_top15_list), each = 2))
```

What is the fraction of AMD genes that belongs to the top 5% predicted targets?  
```{r}
target_prediction_performances_discrete_cv %>% 
  filter(true_target) %>% 
  pull(fraction_positive_predicted) %>% 
  mean()
```

What is the fraction of non-p-AMD genes that belongs to the top 5% predicted targets?  
```{r}
target_prediction_performances_discrete_cv %>% 
  filter(! true_target) %>% 
  pull(fraction_positive_predicted) %>% 
  mean()
```

AMD genes are enriched in the top-predicted target genes. To test this, we apply a Fisher’s exact test for every cross-validation round and report the average p-value.   
```{r}
target_prediction_performances_discrete_fisher <- amd_genes_prediction_top15_list %>% 
  lapply(calculate_fraction_top_predicted_fisher, quantile_cutoff = 0.95)

target_prediction_performances_discrete_fisher %>% unlist() %>% mean()
```

top predicted genes in 5 rounds
```{r}
top_predicted_genes <- seq(length(amd_genes_prediction_top15_list)) %>% 
  lapply(get_top_predicted_genes, amd_genes_prediction_top15_list) %>% 
  purrr::reduce(full_join, by = c("gene", "true_target"))

top_predicted_genes %>% 
  filter(true_target) %>% 
  distinct(gene, .keep_all = T)
```

# infer target genes of top ranked ligands  
```{r}
active_ligand_target_link_df <- best_upstream_ligands %>% 
  lapply(FUN = get_weighted_ligand_target_links, 
         geneset = goi_expressed, 
         ligand_target_matrix = ligand_target_matrix, 
         n = 50) %>% 
  bind_rows()

active_ligand_target_link_df %>% 
  arrange(-weight)
```

```{r}
active_ligand_target_link_df %>% 
  pull(weight) %>% 
  hist(breaks = seq(min(active_ligand_target_link_df$weight, na.rm = T), max(active_ligand_target_link_df$weight, na.rm = T), length.out = 60),
       main = "Distribution of Weight", col = "orange", border = "grey")

abline(v = active_ligand_target_link_df %>% 
         pull(weight) %>% 
         quantile(probs = 0.8, na.rm = TRUE), 
       col = 'red', 
       lwd = 2, 
       lty = 2)
```


```{r}
cols <- colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(100)

ligand_target_heatmap <- active_ligand_target_link_df %>% 
  filter(!is.na(weight)) %>% 
  mutate(m_weight = ifelse(weight > quantile(weight, 0.25), weight, 0)) %>% 
  ggplot() +
  geom_tile(aes(x = reorder(ligand, -m_weight), target, fill = m_weight)) + 
  scale_fill_gradient(name = NULL, low = cols[50], high = cols[100]) +
  scale_x_discrete(name = "ligands") +
  scale_y_discrete(name = "targets") +
  theme(axis.text.x = element_text(angle = -45, hjust = 0)) +
  ggtitle(label = "strength of ligands targets links")  +
  theme(panel.background = NULL, 
        legend.position = "top")

ligand_target_heatmap
saveRDS(object = ligand_target_heatmap, 
        file = "/home/yincy/git/R/Retina/res/ligand_target_heatmap.rds")
```


```{r}
targets <- c("TLR4", "COL10A1", "VEGFA", "TIMP3", "TGFBR1")
```


# expression of beat upstream ligands  
```{r}
# donor 5
donor5_expression <- read.table(file = "/home/yincy/git/Data/AMD-related/AMD-single-cell/GSM4037988/GSM4037988_macula_donor_5_enriched_expression.tsv.gz", 
                                sep = " ", 
                                header = T, 
                                stringsAsFactors = F)
donor5_expression %>% dim()
donor5_expression %>% .[1:5, 1:5]

donor5_expression <- donor5_expression[, -1]
donor5_cell_meta <- donor5_expression[, c(1:3)]

donor5_expression_table <- donor5_expression[, -c(1:3)] %>% 
  t() %>% 
  magrittr::set_colnames(donor5_expression$barcode)

# choriocapillaris endothelial  
donor5_choriocapillaris_endothelial <- donor5_expression_table[, donor5_cell_meta$final_cluster_labels == 7]
donor5_choriocapillaris_endothelial %>% dim()
expressed_genes_choriocapillaris_endothelial <- rownames(donor5_choriocapillaris_endothelial)[apply(donor5_choriocapillaris_endothelial, 1, function(x) mean(x > 0) > 0.1)]

# donor 6
donor6_expression <- read.table(file = "/home/yincy/git/Data/AMD-related/AMD-single-cell/GSM4037989/GSM4037989_macula_donor_6_enriched_expression.tsv.gz", 
                                sep = " ", 
                                header = T, 
                                stringsAsFactors = F)
donor6_expression %>% dim()
donor6_expression %>% .[1:5, 1:5]

donor6_expression <- donor6_expression[, -1]
donor6_cell_meta <- donor6_expression[, c(1:3)]

donor6_expression_table <- donor6_expression[, -c(1:3)] %>% 
  t() %>% 
  magrittr::set_colnames(donor6_expression$barcode)

# choriocapillaris endothelial  
donor6_choriocapillaris_endothelial <- donor6_expression_table[, donor6_cell_meta$final_cluster_labels == 7]
donor6_choriocapillaris_endothelial %>% dim()
expressed_genes_choriocapillaris_endothelial <- rownames(donor6_choriocapillaris_endothelial)[apply(donor6_choriocapillaris_endothelial, 1, function(x) mean(x > 0) > 0.1)]

# donor 7 
donor7_expression <- read.table(file = "/home/yincy/git/Data/AMD-related/AMD-single-cell/GSM4037990/GSM4037990_macula_donor_7_enriched_expression.tsv.gz", 
                                sep = " ", 
                                header = T, 
                                stringsAsFactors = F)
donor7_expression %>% dim()
donor7_expression %>% .[1:5, 1:5]

donor7_expression <- donor7_expression[, -1]
donor7_cell_meta <- donor7_expression[, c(1:3)]

donor7_expression_table <- donor7_expression[, -c(1:3)] %>% 
  t() %>% 
  magrittr::set_colnames(donor7_expression$barcode)

# choriocapillaris endothelial  
donor7_choriocapillaris_endothelial <- donor7_expression_table[, donor7_cell_meta$final_cluster_labels == 7]
donor7_choriocapillaris_endothelial %>% dim()
expressed_genes_choriocapillaris_endothelial <- rownames(donor7_choriocapillaris_endothelial)[apply(donor7_choriocapillaris_endothelial, 1, function(x) mean(x > 0) > 0.1)]
```


```{r, message=F}
best_upstream_ligands_expression_df <- cbind(
  donor4_expression_table[best_upstream_ligands, donor4_cell_meta$final_cluster_labels == 7], 
  donor5_expression_table[best_upstream_ligands, donor5_cell_meta$final_cluster_labels == 7], 
  donor6_expression_table[best_upstream_ligands, donor6_cell_meta$final_cluster_labels == 7], 
  donor7_expression_table[best_upstream_ligands, donor7_cell_meta$final_cluster_labels == 7]
)

expression_ligands_ridges <- best_upstream_ligands_expression_df %>% 
  as.data.frame() %>% 
  rownames_to_column("ligands") %>% 
  gather(key = "cells", value = "expression", -ligands) %>% 
  mutate(group = ifelse(substr(cells, 18, 18) == '1', "AMD", "Normal"), 
         ligands = factor(ligands, levels = rev(best_upstream_ligands))) %>% 
  ggplot(aes(expression, ligands)) +
  geom_density_ridges(aes(fill = group)) +
  scale_fill_manual(name = NULL, values = c("green", "grey80")) +
  theme_classic() +
  scale_x_continuous(name = "relative expression") +
  scale_y_discrete(name = "top ligands")

expression_ligands_ridges
saveRDS(object = expression_ligands_ridges, 
        file = "/home/yincy/git/R/Retina/res/expression_ligands_ridges.rds")
```

# expression of targets  
```{r}
statistic_significance_targets <- fit_cont %>% 
  as.data.frame() %>% 
  arrange(p.value) %>% 
  dplyr::filter(genes.geneSymbol %in% targets) %>% 
  ggplot(aes(reorder(genes.geneSymbol, log10(p.value)), -log10(F.p.value))) +
  geom_bar(stat = "identity", fill = c("grey30", "blue", rep("grey30", 3))) +
  coord_flip() +
  scale_x_discrete(name = NULL) +
  scale_y_continuous(breaks = c(0, 1, 2, 3) %>% round(digits = 1), 
                     labels = c(0.0, 1.0, 2, 3)) +
  ggtitle(label = "significance of targets") +
  theme_classic()

statistic_significance_targets
saveRDS(object = statistic_significance_targets, 
        file = "/home/yincy/git/R/Retina/res/statistic_significance_targets.rds")
```


```{r}
expression_of_targets_boxplot <- y_filtered %>% edgeR::cpm() %>% .[y_filtered$genes$geneSymbol %in% targets, ] %>% 
  as.data.frame() %>% 
  rownames_to_column("ensembl") %>% 
  left_join(gs[gs$geneSymbol %in% targets, ], by = c('ensembl' = "id")) %>% 
  dplyr::select(geneSymbol, contains("TR")) %>% 
  gather(key = "sample", value = "expression", -geneSymbol) %>% 
  mutate(group = ifelse(sample %in% early_amd_samples, "Early AMD", "Normal"), 
         geneSymbol = factor(geneSymbol, levels = targets)) %>% 
  ggplot(aes(reorder(geneSymbol, expression), expression)) +
  geom_boxplot(aes(color = group)) + 
  geom_jitter(aes(color = group), show.legend = F, width = 0.1) +
  scale_x_discrete(name = NULL) +
  scale_y_continuous(name = "relative expression") +
  facet_wrap(. ~ geneSymbol, scales = "free", nrow = 1) +
  scale_color_discrete(name = NULL) +
  theme(legend.position = "top", 
        panel.background = NULL, 
        axis.ticks.length.x = unit(x = 0, units = "cm"), 
        axis.text.x = element_text(size = 0))

expression_of_targets_boxplot
saveRDS(object = expression_of_targets_boxplot, 
        file = "/home/yincy/git/R/Retina/res/expression_targets_RPE_boxplot.rds")
```

# expression of regulator  
```{r}
y_filtered <- readRDS(file = "/home/yincy/git/R/Retina/res/GSE99248_y_filtered.rds")
expression_regulators <- y_filtered %>% edgeR::cpm() %>% .[y_filtered$genes$geneSymbol %in% c("RUNX2", "AR", "ESR1", "SMAD3"), ] %>% 
  as.data.frame() %>% 
  rownames_to_column("ensembl") %>% 
  left_join(gs[gs$geneSymbol %in% c("RUNX2", "AR", "ESR1", "SMAD3"), ], by = c('ensembl' = "id")) %>% 
  dplyr::select(geneSymbol, contains("TR")) %>% 
  gather(key = "sample", value = "expression", -geneSymbol) %>% 
  mutate(group = ifelse(sample %in% early_amd_samples, "Early AMD", "Normal"), 
         geneSymbol = factor(geneSymbol, levels = c("RUNX2", "AR", "ESR1", "SMAD3"))) %>% 
  ggplot(aes(reorder(geneSymbol, expression), expression)) +
  geom_boxplot(aes(color = group)) + 
  geom_jitter(aes(color = group), show.legend = F, width = 0.1) +
  scale_x_discrete(name = NULL) +
  scale_y_continuous(name = "relative expression") +
  facet_wrap(. ~ geneSymbol, scales = "free", nrow = 1) +
  scale_color_discrete(name = NULL) +
  theme(legend.position = "top", 
        panel.background = NULL, 
        axis.ticks.length.x = unit(x = 0, units = "cm"), 
        axis.text.x = element_text(size = 0))

expression_regulators
saveRDS(object = expression_regulators, file = "/home/yincy/git/R/Retina/res/expression_regulators.rds")
```

```{r}
statistic_significance_regulator <- fit_cont %>% 
  as.data.frame() %>% 
  arrange(p.value) %>% 
  filter(genes.geneSymbol %in% c("RUNX2", "ESR1", "SMAD3")) %>% 
  ggplot(aes(reorder(genes.geneSymbol, log10(p.value)), -log10(F.p.value))) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_x_discrete(name = NULL) +
  scale_y_continuous(breaks = c(0, 1, 2, 3) %>% round(digits = 1), 
                     labels = c(0.0, 1.0, 2, 3)) +
  ggtitle(label = "significance of regulator") +
  theme_classic()

statistic_significance_regulator
saveRDS(object = statistic_significance_regulator, file = "/home/yincy/git/R/Retina/res/statistic_significance_regulator.rds")
```



# ligands targets links in circos  
```{r}
circos_vis <- active_ligand_target_link_df %>% 
  dplyr::filter(!is.na(weight)) %>% 
  dplyr::filter(weight > quantile(active_ligand_target_link_df %>% pull(weight), probs = 0.2, na.rm = T))

cols <- brewer.pal(n = 3, name = "Dark2")[1:2]

ligand_col <- rep(cols[1], circos_vis %>% pull(ligand) %>% unique() %>% length())
names(ligand_col) <- circos_vis %>% pull(ligand) %>% unique()

target_col <- rep(cols[2], circos_vis %>% pull(target) %>% unique() %>% length())
names(target_col) <- circos_vis %>% pull(target) %>% unique()

width_between_ligand_target <- 10
width_between_sectors <- 2

gaps <- c(
  rep(width_between_sectors, times = circos_vis %>% pull(ligand) %>% unique() %>% length()  - 1), 
  
  width_between_ligand_target, 
  
  rep(width_between_sectors, times = circos_vis %>% pull(target) %>% unique() %>% length()  - 1), 
  
  width_between_ligand_target
)
```

```{r}
tiff("/home/yincy/git/R/Retina/res/ligand_targets_in-circos.tiff", width = 800, height = 800)
lim = 1.3
circos.par(canvas.xlim = c(-lim, lim), canvas.ylim = c(-lim, lim), gap.degree = gaps)
chordDiagram(x = circos_vis, 
             directional = 1, 
             direction.type = c("arrows"), 
             link.arr.type = "big.arrow", 
             grid.col = c(ligand_col, target_col), 
             preAllocateTracks = list(track.height = 0.0075), 
             annotationTrack = "grid", 
             link.sort = T)

circos.track(track.index = 1, 
             panel.fun = function(x, y){
               circos.text(x = CELL_META$xcenter, 
                           y = CELL_META$ycenter, 
                           labels = CELL_META$sector.index, 
                           facing = "clockwise", 
                           niceFacing = TRUE, 
                           adj = c(0, 0.5), 
                           cex = 0.6)
             }, 
             bg.border = NA)

legend(x = 1, y = -0.8, 
       legend = c("ligands", "targets"), 
       pch = 15, 
       col = c(ligand_col %>% unique(), target_col %>% unique()), 
       cex = 1, 
       bty = "n")

dev.off()
circos.clear()
```


# Visualization signaling network with igraph  
```{r}
weighted_network <- readRDS(file = "/home/yincy/git/Data/NicheNet/data/weighted_networks.rds")
ligand_tf_matrix <- readRDS(file = "/home/yincy/git/Data/NicheNet/data/ligand_tf_matrix.rds")

lr_network <- readRDS(file = "/home/yincy/git/Data/NicheNet/data/lr_network.rds")
sig_network <- readRDS(file = "/home/yincy/git/Data/NicheNet/data/signaling_network.rds")
gr_network <- readRDS(file = "/home/yincy/git/Data/NicheNet/data/gr_network.rds")
```

```{r}
ligand_all <- "TGFB1"
target_all <- "COL10A1"

TGFB1_COL10A1_signaling_network <- get_ligand_signaling_path(
  ligand_tf_matrix = ligand_tf_matrix, 
  ligands_all = ligand_all, 
  targets_all = target_all, 
  weighted_networks = weighted_network, 
  top_n_regulators = 4
)

TGFB1_COL10A1_signaling_network_min_max <- TGFB1_COL10A1_signaling_network

TGFB1_COL10A1_signaling_network_min_max$sig <- TGFB1_COL10A1_signaling_network_min_max$sig %>% 
  mutate(weight = (weight - min(weight))/(max(weight) - min(weight)) + 0.75)

TGFB1_COL10A1_signaling_network_min_max$gr <- TGFB1_COL10A1_signaling_network_min_max$gr %>% 
  mutate(weight = (weight - min(weight))/(max(weight) - min(weight)) + 0.75)
```


```{r}
path_to_vis <- bind_rows(TGFB1_COL10A1_signaling_network_min_max$sig, TGFB1_COL10A1_signaling_network_min_max$gr)

path_to_vis <- aggregate(path_to_vis[, 3], by = path_to_vis[, 1:2], sum)
net <- graph_from_data_frame(d = path_to_vis)

vcol <- grep("grey70", vcount(net))
vcol[V(net)$name == "TGFB1"] <- "tomato"
vcol[V(net)$name %in% c("COL10A1")] <- "steelblue"
vcol[V(net)$name %in% c("AR", "ESR1", "RUNX2")] <- "green"
vcol[is.na(vcol)] <- "grey70"

tk <- tkplot(graph = net)
tk_coord <- tkplot.getcoords(tkp.id = tk, norm = T)
tk_close(tkp.id = tk)
```

```{r}
tiff(filename = "/home/yincy/git/R/Retina/res/TGFB1-COL10A1-signaling-network.tiff")
par(mar = c(0, 0, 4, 0), bg = "white", cex.main = 0.8)
plot(net, 
     vertex.color = vcol, 
     vertex.label.color = "black",
     layout = tk_coord * 3.5, 
     edge.width = E(net)$weight * 2, 
     edge.arrow.size = 0.8, 
     vertex.label.dist = 0, 
     vertex.size = 20, 
     vertex.label.cex = 1, 
     vertex.shape = "circle", 
     vertex.frame.color = NA,
     rescale = F, 
     xlim = c(-2, 2), 
     ylim = c(-2, 2), 
     vertex.label.color = "white", 
     main = "TGFB1 COL10A1 signaling network")

legend("bottomleft", 
       legend = c("ligand", "regulator", "target"), 
       pch = 19, 
       col = c("tomato", "green", "steelblue"), 
       bty = "n")
dev.off()
```



# Infering supported source  
```{r}
data_source_net_TGFB1_COL10A1 <- infer_supporting_datasources(
  signaling_graph_list = TGFB1_COL10A1_signaling_network_min_max, 
  lr_network = lr_network, 
  sig_network = sig_network, 
  gr_network = gr_network
)

data_source_net_TGFB1_COL10A1
```

```{r}
write.csv(x = data_source_net_TGFB1_COL10A1, 
          file = "/home/yincy/git/R/Retina/res/supporting_datasource_TGFB1_COL10A1.csv")
```



